Stable quantum memories with \CMH{\sout{few} limited} measurement\CMH{\sout{s}}

### 2017-05-19 IsingECC/manuscript_ising_ecc_CMH_comments.tex
Added manucript with my comments

\usepackage{listings}
\usepackage{cancel}

@@

@@

\title{Stable quantum memories with few measurements}
%\title{Finite temperature thresholds for stabilizer codes with few measurements}

@@

Building off this previous work, here we examine the extent to which a limited amount of measurement can increase the lifetime of stabilizer codes with string-like excitations.  In sum, we demonstrate an algorithm that, for any constant density of measurements for a stabilizer code with stringlike excitations undergoing dissipation at a fixed temperature, a threshold can be achieved.  The threshold temperature scales with the amount of measurement used---fewer measurements result in a smaller threshold temperature, whereas more complete measurement raises the threshold temperature.  This tradeoff is commensurate with and complements what is known about decoding the stabilizer codes in the presence of \emph{noisy}, but complete measurements.

@@

where, for the remainder of the manuscript, unless explicitly stated otherwise, we assume $\Delta=1$.  This also fixes our units for temperature.  This is exactly the Hamiltonian version of the repetition stabilizer \emph{code}\cite{Freeman2016}.  Note that the terms $\sigma^i_z \sigma^{i+1}_z$ exactly correspond to the parity check stabilizer operators of the repetition code.  Confer with Table \ref{tab:code_vs_hamiltonian} for the correspondences between the stabilizer Hamiltonian and stabilizer code versions of the 1d Ising model.

@@

In the parlance of the 1D Ising model, bit flip errors are often also classified via the dual variables called \emph{domain walls}.  Domain walls are simply locations on the 1D Ising chain where a stabilizer operator yields a measurement of $-1$---i.e., locations where neighboring spins point in different directions.  With periodic boundary, the number of these locations is always a multiple of two, and a single bit flip event either creates a pair of such domain walls, deletes a pair of domain walls, or causes a domain wall to translate by one unit.

Whether considered as a code or as a Hamiltonian, the condition for whether a state of the system with errors present can be reliably returned to an encoded state is the same: so long as less than half the system has had errors, a majority rule decoder that has access to measurements of the full set of stabilizers ${\sigma^i_z \sigma^{i+1}_z}$ will reliably be able to correctly remove errors.  When errors are completely independent (i.e., at very high temperature), we can define random variables $x_i=1$ when an error occurs on site $i$, and $0$ otherwise.  If these errors occur with probability $p$ on each spin, independently at random every error detection cycle, then Chernoff's bound gives an upper bound to the probability of an error in the encoded space, $P(\Sigma_i x_i \geq L/2) \leq \rm{exp}[-Lp\frac{\delta^2}{2+\delta}]$ for $\delta=1/2p-1$.  Thus, for complete measurement, errors in the encoded subspace are exponentially suppressed in system size, so long as the error rate is sufficiently small.

@@

 The main consequence of choosing an Ohmic bath is that it sets the amplitude of the excitation hopping process.  That is, $\gamma(0)$ is determined by the $\omega \rightarrow 0$ limit of the spectral density of the bath, and for the Ohmic bath taking the $\omega\rightarrow0$ limit of  Eq. \ref{eq:gammadef} yields $\gamma(0) \sim T$. 
Ultimately, this means that the hopping rate of domains walls is controlled by this choice of bath model. At finite temperatures, this introduces correlations into the patterns of errors that effect the system, and so it is no longer possible to talk about an ``independent error probability per site''. 
In contrast to the behavior of $\gamma(0)$, 
the other operationally important feature of the bath, the ratio of domain wall creation and annihilation rates, is set by detailed balance to Boltzmann-like scaling (i.e., $\gamma(1)/\gamma(-1) = \exp(-1/T)$), and is independent of the choice of bath spectrum.

 In the most extreme case, at sufficiently low temperature, errors are most often immediately dissipated by the bath upon creation.  However, because domain walls that are not immediately adjacent cannot be dissipated by the bath, the system occasionally becomes ``trapped'' in the first excited state by a rare pair creation followed by pair hopping event -- i.e., a $D^\dagger_{b}$ followed by a $T_{b}$ -- before the bath can dissipate the excitation.  Then any subsequent errors are overwhelmingly more likely to act on existing pair of domain walls, translating them around in a one-dimensional random walk.

 Thus, error correction for the 1D Ising model at low temperature with this sort of bath dynamics is equivalent to attempting to identify these randomly-migrating rare pairs of domain walls.  While a majority-rule decoding scheme works in both low and high temperature limits for the Ising model, if the number of measurement resources is restricted, the standard majority rule scheme breaks down.

@@

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{detect_swap.pdf}}
\end{center}
\caption{This cartoon illustrates the ``centering'' procedure for detected defects.  Spin variables are in gray, and domain wall variables are in blue (no defect present) and red (defect present).  When a defect is detected on a measurement patch (blue box), it is swapped to the center of the measurement patch via the $\rm{DSWAP}$ operator (black arrows).  The defect immediately adjacent to it is also swapped onto the measurement patch so as not to pull apart defect pairs that would have otherwise dissipated.}
\label{fig:detect_swap}
\end{figure}

@@

To perform error correction properly, we need to be able to estimate the probability that two given measured defects are a pair, given that they have been measured at two particular measurement patches at two different times.  For notational convenience, we define:
\begin{align}
d_1 : d_2 \equiv {\rm defect}\ d_1\ {\rm and}\ d_2\ {\rm are\ a\ pair}
\end{align}
and
\begin{align}
d_i^{x_1,t_1} \equiv {\rm defect}\ d_i\ {\rm measured\ at\ time}\ t_1\ {\rm at\ patch}\ x_1
\end{align}

@@

To calculate this probability, we proceed via Bayes rule: 
\begin{align}
\label{eq:bayes}
&P(d_1:d_2 | d_1^{x_1,t_1} \wedge d_2^{x_2,t_2}) = \\ \notag
&\frac{P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) P(d_1 : d_2)}{P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})}
\end{align}
The individual terms on the right hand side of equation \ref{eq:bayes} are straightforward to interpret.  $P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2)$ represents the probability that two measured defects would be at $(x_1,t_1)$ and $(x_2,t_2)$ given that they are indeed a pair.  This can be related to the probability that a one dimensional diffusion process with diffusion constant $D$ will perform an excursion of distance $|x_2-x_1|$ or greater in a time $t_2 - t_1$; \textit{i.e.,} will perform an excursion that can measurement patches at $x_1$ and $x_2$. Explicitly,
\begin{align}
\label{eq:bayesformula}
&P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) \\ \notag
&= 1-2\int_{0}^{|x_2-x_1|} dx \frac{1}{2\pi D |t_2-t_1|} \rm{exp}\bigg(-\frac{|x_2-x_1|^2}{2 D |t_2-t_1|}\bigg) \\ \notag 
&= 1 - {\rm erf}\bigg(\frac{|x_2-x_1|}{2\sqrt{D |t_2 - t_1|}}\bigg) 
\end{align}
For our analysis, we will choose $D\propto \gamma_0$.  The exact correspondence between $D$ and $\gamma_0$ depends on the details of the error correction algorithm itself, so, in practice, we treat the constant of proportionality as an empirically tuned parameter.  Furthermore, we approximate any detected defects as arising from a pair that was created an equal distance between the measurement patches at locations $x_1$ and $x_2$ for the purposes of calculating the probability in Eq. \ref{eq:bayesformula}.

$P(d_1 : d_2)$ represents the probability that two measured defects, $d_1$ and $d_2$, are in fact a pair.  Finally, $P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})$ is the probability that two defects are measured, one at $(x_1,t_1)$, and the other at $(x_2,t_2)$.  As we discuss in Appendix \ref{sec:bayesdecoder}, these factors are not as important for the decoding scheme as Eq. \ref{eq:bayesformula}.  In practice, we find that using the expression from Eq. \ref{eq:bayesformula} alone is sufficient to provide resilient error correction.  We defer further discussion to the appendix.

@@

 The two primary failure modes of the error correction procedure are (1) defects escaping measurement patches, and (2) defects being paired incorrectly. These failure modes become more harmful as temperature increases.  Failure mode 1 can be suppressed by working with large measurement patches, as the escape timescale is exponential in the number of sites within the measurement patch---i.e., it scales like $(1/\gamma_0)^{\rm{\#\ of\ sites\ on\ patch}}$.  Failure mode 2 can be suppressed to a degree, but at high enough temperature, will eventually happen with high probability, as is the case in the full-measurement version of the protocol.  If too many errors are introduced between measurement cycles, it becomes impossible to correct the system even in principle because the syndrome measurements can no longer be unambiguously decoded.  At sufficiently low temperature, however, with some assumptions, our algorithm can extend the lifetime of the system exponentially in system size.

 Suppose that (a) defects are efficiently trapped by the measurement patches, and (b) temperature is low so that there is $\rho \ll 1$ defect pair per measurement patch.  In this regime, condition (a) guarantees that defects do not escape measurement patches.  Then, the only error pathway is a sequence of incorrect, but nonetheless ``plausible'' error correction operations, whereby some sdefects are paired with defects that are not their own pair.  
%************************Make explicit here that it's a heuristic argument.  Because the error processes in our model are difficult to etc. etc. etc.
 To upper bound this error rate, note that such erroneous pairing occurs because one member of a paired defect has not yet been measured.  In other words, one defect of a pair is measured, and the other defect spends ``too long'' migrating around in the unmeasured bulk region.  Suppose that the average amount of time a defect spends sitting on a measurement patch is $\tau_s$, and the average time it takes a defect to be detected on a measurement patch, after creation, is $\tau_d$.  Further suppose $\tau_s/\tau_d = \delta \ll 1$---that is, on average, defects are unlikely to escape from a measurement patch over the timescale it takes a defect to migrate within the bulk region to a measurement patch.

 Treating the full dynamics of errors is difficult, so we first consider a different, simpler error dynamics.  First, we argue how, in the presence of this simpler error model, our algorithm provides an exponentially long lifetime in system size.  Then, we argue how this simpler error model is actually more pessimistic with respect to possible error processes than the true error dynamics---that is, we expect the real model to have a \emph{better} lifetime scaling than would be expected from the simple error model.

 The simple error model is defined as follows:  suppose that a single pair of defects is in a system, and that no new pairs will be introduced.  One of the pair is fixed on a measurement rail, and the other is, at time 0, undetected.  Further, suppose that there is an error process that occasionally translates the unmeasured defect by an amount $2\sqrt{\gamma_0 \delta t}$, for hopping rate $\gamma_0$ and for system time $\delta t$.  Note that this means the error process acts on longer distance scales as system time increases.  The particular form of this error process is chosen to mimic a spurious error correction event, where a pair of defects is ``corrected'', but this pair of defects was not a real pair, leaving another unmeasured defect even further away.  As time increases, the characteristic distance over which this error process could occur also increases, in accordance with the typical pair-wise separation between two defects performing a random walk.  This typical distance is exactly the factor used by the error correction algorithm to determine if a pair of defects should be corrected or not.  Thus, the error process is representative of a worst case error correction event that not only pairs the wrong two defects, but leaves the system in a configuration with an unmeasured defect as far separated from the measured defect as possible.

 If this error process happens every $\tau_{\epsilon}$, then an uncorrectable error will occur if the bulk defect remains undetected up until it crosses half the system.  For patches of size $\lambda$, the probability that this occurs is roughly $(\tau_{\epsilon} / \tau_d)^{k}$, where $k$ is the number of times the error process must occur for the error process to have separated the defects a distance $(L/2\lambda)$ and $\tau_d$ is the timescale associated with a non-erroneous error correction operation.  Because this error process happens approximately every $\tau_{\epsilon}$, after a timescale $q*\tau_{\epsilon}$, the defect pairs will have been separated a distance $\Sigma^q_{i=1} \sqrt{i * \gamma_0 \tau_{\epsilon}}$, assuming that they are never correctly paired.  This sum $\Sigma^q_{i=1} \sqrt{i}$ grows asymptotically like $q^{3/2}$.  Thus, $k$ then scales approximately like $(L/\lambda)^{2/3}$.

 Finally, if we have $L/\lambda$ such simultaneous error processes independently in the system---one for each measurement patch---then the total error probability scales like
\begin{align}
\label{eq:err_scaling}
 P(\rm{uncorrectable\ error}) \leq (L/\lambda) (\tau_{\epsilon} / \tau_d)^{(L/\lambda)^{2/3}}.
\end{align}

For this system, $\tau_{\epsilon}$ is much smaller than $\tau_d$, thus the full probability of erroneous corrective operations is exponentially small in system size.

 This probability serves as an upper bound because it is extremely pessimistic about the sorts of error processes occurring.  Note that in the real system, a spurious error correction process that effectively increases the distance between a pair of defects also reduces the total number of defects by two.  Thus, while our toy error model is ``non-interacting''---that is, it assumes $L/\lambda$ independent error processes which, in sum, take the form described in Eq. \ref{eq:err_scaling}---a more careful treatment of the error process, including interactions between defects, as in the real model, would result in an error probability \emph{smaller} than the one calculated here.

 In the following section, we provide numerical evidence that the lifetime of the Ising model in the presence of the protocol scales quasi-exponentially with the number of measurement patches, as anticipated by the upper bound in Eq.\ref{eq:err_scaling}.

@@

In this section, we examine the behaviour of the protocol at different system sizes, temperatures, and measurement fractions.  While data is reported in terms of system size, the more fundamental length scale is the characteristic size of the \emph{measurement patch}.  This is because the size of the measurement patch is the shortest length scale relevant to the algorithm, and thus controls the majority of the scaling behavior.  Perhaps unsurprisingly, systems of radically different size but with the same number of measurement patches have fairly comparable lifetimes (e.g., size 200 system with 10 patches versus size 100 system with 10 patches).  We elaborate on the scaling of the measurement fractions further in the discussion.  Unless otherwise noted, the data reported here are for systems with 3 measured sites for every 7 sites for a measurement fraction of $3/7$.  Thus, the total size of unit cell is $\lambda=7$, there are $\lambda_m=3$ measured sites, and $\lambda_b=4$ bulk sites, as is depicted in Fig. \ref{fig:detect_swap}.

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{LifetimeVsTemperature.pdf}}
\end{center}
\caption{Lifetime of various system sizes as a function of temperature.  Measurement fraction is $3/7$.  Notice the transition between no-effect, and significant lifetime improvement near $T=.16$.  A $3/7$ measurement fraction was used for this data.}
\label{fig:LifetimeVsTemperature}
\end{figure}

\figref{fig:LifetimeVsTemperature} depicts the scaling of the system lifetime with temperature.  At low temperatures, the system lifetime increases dramatically with both lower temperatures, and larger system size.  Due to finite size effects, it is difficult to extract an unambiguous threshold temperature, but below $T\approx.13$, the lifetime manifestly increases with larger system size.  We empirically define a threshold temperature by the choosing a large system size, fitting a curve to the Lifetime versus Temperature data which results in a lifetime improvement greater than a factor of $10$, and then back-extrapolating where this curve crosses the Temperature axis.

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{LifetimeVsSystemSize.pdf}}
\end{center}
\caption{Lifetime of the Ising model at various temperatures plotted against system size.  Note the monotonic growth in lifetime for low temperature models, as well as the plateau in lifetime for moderately sized systems. A $3/7$ measurement fraction was used for this data.}
\label{fig:LifetimeVsSystemSize}
\end{figure}

>>>>

\usepackage{listings}
\usepackage{cancel}
\usepackage{ulem}

@@

\newcommand{\CMH}[1]{{\color{green} { #1}}}

@@

\title{Stable quantum memories with \CMH{\sout{few} limited} measurement\CMH{\sout{s}}}
%\title{Finite temperature thresholds for stabilizer codes with few measurements}

@@

Building off this previous work, here we examine the extent to which a limited amount of measurement can increase the lifetime of stabilizer codes with string-like excitations.  In sum, we demonstrate an algorithm that, for any \CMH{\it{(do we know this?)}} constant density of measurements for a stabilizer code with stringlike excitations undergoing dissipation at a fixed temperature, a threshold can be achieved.  The threshold temperature scales with the amount of measurement used---fewer measurements result in a smaller threshold temperature, whereas more complete measurement raises the threshold temperature.  This tradeoff is commensurate with and complements what is known about decoding the stabilizer codes in the presence of \emph{noisy}, but complete measurements.

@@

where, for the remainder of the manuscript, unless explicitly stated otherwise, we assume $\Delta=1$.  \CMH{\sout{This also fixes our units for temperature}}.  This is exactly the Hamiltonian version of the repetition stabilizer \emph{code}\cite{Freeman2016}.  Note that the terms $\sigma^i_z \sigma^{i+1}_z$ exactly correspond to the parity check stabilizer operators of the repetition code \CMH{(see Table \ref{tab:code_vs_hamiltonian})}.  \CMH{\sout{Confer with Table \ref{tab:code_vs_hamiltonian} for the correspondences between the stabilizer Hamiltonian and stabilizer code versions of the 1d Ising model}}.

@@

In the parlance of the 1D Ising model, bit flip errors are often also classified via the dual variables called \emph{domain walls}.  Domain walls are simply locations on the 1D Ising chain where a stabilizer operator yields a measurement of $-1$---i.e., locations where neighboring spins point in different directions.  With periodic boundary, the number of these locations is always \CMH{\sout{a multiple of two} even}, and a single bit flip event either creates a pair of such domain walls, deletes a pair of domain walls, or causes a domain wall to translate by one unit.

\CMH{\sout{Whether considered as a code or as a Hamiltonian, the condition for whether a state of the system with errors present can be reliably returned to an encoded state is the same:}} so long as less than half the system has had errors, a majority rule decoder that has access to measurements of the full set of stabilizers ${\sigma^i_z \sigma^{i+1}_z}$ will reliably be able to correctly remove errors.  When errors are completely independent (i.e., at very high temperature), we can define random variables $x_i=1$ when an error occurs on site $i$, and $0$ otherwise.  If these errors occur with probability $p$ on each spin, independently at random every error detection cycle, then Chernoff's bound gives an upper bound to the probability of an error in the encoded space, $P(\Sigma_i x_i \geq L/2) \leq \rm{exp}[-Lp\frac{\delta^2}{2+\delta}]$ for $\delta=1/2p-1$.  Thus, for complete measurement, errors in the encoded subspace are exponentially suppressed in system size, so long as the error rate is sufficiently small.

@@

 The main consequence of choosing an Ohmic bath is that it sets the amplitude of the excitation hopping process.  That is, $\gamma(0)$ is determined by the $\omega \rightarrow 0$ limit of the spectral density of the bath, and for the Ohmic bath taking the $\omega\rightarrow0$ limit of  Eq. \ref{eq:gammadef} yields $\gamma(0) \sim T$. 
Ultimately, this means that the hopping rate of domains walls is controlled by this choice of bath model. At finite temperatures, this introduces correlations into the patterns of errors that effect the system, and so it is no longer possible to talk about an ``independent error probability per site''. 
In contrast to the behavior of $\gamma(0)$, 
the other operationally important feature of the bath, the ratio of domain wall creation and annihilation rates, is set by detailed balance to Boltzmann-like scaling (i.e., $\gamma(1)/\gamma(-1) = \exp(-1/T)$), and is independent of the choice of bath spectrum. \CMH{\it{Is the above discussion necessary?}}

 In the most extreme case, at sufficiently low temperature, \CMH{\sout{errors} pairs of neighboring domain walls} are most often immediately dissipated by the bath upon creation.  However, \CMH{\sout{because domain walls that are not immediately adjacent cannot be dissipated by the bath, the system occasionally becomes ``trapped'' in the first excited state by a rare} if a} pair creation \CMH{is} followed by pair hopping event -- i.e., a $D^\dagger_{b}$ followed by a $T_{b}$ -- \CMH{\sout{before the bath can dissipate the excitation} the error can no longer be immediately dissipated by the local action of the bath. \sout{Then any subsequent errors are overwhelmingly more likely to act on existing pair of domain walls, translating them around in} Subsequently the domain walls will undergo} a one-dimensional random walk\CMH{, and topologically non-trivial random walks will cause uncorrectable logical errors}.

 Thus, error correction for the 1D Ising model at low temperature with this sort of bath dynamics \CMH{\sout{is equivalent to} requires} attempting to identify these randomly-migrating rare pairs of domain walls.  While a majority-rule decoding scheme works in both low and high temperature limits for the Ising model, if the number of measurement resources is restricted, the standard majority rule scheme breaks down.

@@

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{detect_swap.pdf}}
\end{center}
\caption{This cartoon illustrates the ``centering'' procedure for detected defects.  Spin variables are in gray, and domain wall variables are in blue (no defect present) and red (defect present).  When a defect is detected on a measurement patch (blue box), it is swapped to the center of the measurement patch via the $\rm{DSWAP}$ operator (black arrows).  The defect immediately adjacent to it is also swapped onto the measurement patch so as not to pull apart defect pairs that would have otherwise dissipated. \CMH{\it{Put $\lambda$ and $\lambda_m$ in this figure graphically}}}
\label{fig:detect_swap}
\end{figure}

@@

To perform error correction properly, we need to be able to estimate the probability that two given measured defects \CMH{\it{Have you switched from "domain wall" terminology to "defect"?}} are a pair, given that they have been measured at two particular measurement patches at two different times.  For notational convenience, we define:
\begin{align}
d_1 : d_2 \equiv {\rm defect}\ d_1\ {\rm and}\ d_2\ {\rm are\ a\ pair}
\end{align}
and
\begin{align}
d_i^{x_1,t_1} \equiv {\rm defect}\ d_i\ {\rm measured\ at\ time}\ t_1\ {\rm at\ patch}\ x_1
\end{align}

@@

To calculate this probability, we proceed via Bayes rule: 
\begin{align}
\label{eq:bayes}
&P(d_1:d_2 | d_1^{x_1,t_1} \wedge d_2^{x_2,t_2}) = \\ \notag
&\frac{P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) P(d_1 : d_2)}{P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})}
\end{align}
The individual terms on the right hand side of equation \ref{eq:bayes} are straightforward to interpret.  $P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2)$ represents the probability that two measured defects would be at $(x_1,t_1)$ and $(x_2,t_2)$ given that they are indeed a pair.  This can be related to the probability that a one dimensional diffusion process with diffusion constant $D$ will perform an excursion of distance $|x_2-x_1|$ or greater \CMH{\it{Why or greater? Shouldn't it be exactly $x_2-x_1$?}} in a time $t_2 - t_1$; \textit{i.e.,} will perform an excursion that can measurement patches at $x_1$ and $x_2$. Explicitly,
\begin{align}
\label{eq:bayesformula}
&P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) \\ \notag
&= 1-2\int_{0}^{|x_2-x_1|} dx \frac{1}{2\pi D |t_2-t_1|} \rm{exp}\bigg(-\frac{|x_2-x_1|^2}{2 D |t_2-t_1|}\bigg) \\ \notag 
&= 1 - {\rm erf}\bigg(\frac{|x_2-x_1|}{2\sqrt{D |t_2 - t_1|}}\bigg) 
\end{align}
For our analysis, we will choose $D\propto \gamma_0$.  The exact correspondence between $D$ and $\gamma_0$ depends on the details of the error correction algorithm itself, so, in practice, we treat the constant of proportionality as an empirically tuned parameter.  Furthermore, we approximate any detected defects as arising from a pair that was created an equal distance between the measurement patches at locations $x_1$ and $x_2$ for the purposes of calculating the probability in Eq. \ref{eq:bayesformula}.

$P(d_1 : d_2)$ represents the probability that two measured defects, $d_1$ and $d_2$, are in fact a pair \CMH{\it{What do you mean by your notation $d_1$ and $d_2$ here? I.e. what does the subscript mean in the absence of an "$x$" or "$t$"?}}.  Finally, $P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})$ is the probability that two defects are measured, one at $(x_1,t_1)$, and the other at $(x_2,t_2)$.  As we discuss in Appendix \ref{sec:bayesdecoder}, these factors are not as important for the decoding scheme as Eq. \ref{eq:bayesformula}.  In practice, we find that using the expression from Eq. \ref{eq:bayesformula} alone is sufficient to provide resilient error correction.  We defer further discussion to the appendix.

@@

 \CMH{\it{I'm concerned this section is no sufficiently precise--perhaps it should be condensed}}

 The two primary failure modes of the error correction procedure are (1) defects escaping measurement patches, and (2) defects being paired incorrectly. \CMH{Both }These failure modes become more \CMH{\sout{harmful} probable} as temperature increases.  Failure mode 1 can be reduced by increasing the size of the measurement patches; \CMH{\sout{suppressed by working with large measurement patches, as}} the escape timescale is exponential in the \CMH{\sout{number of sites within the measurement patch} size $\lambda$ of the measurement patches, \sout{---i.e., it scales like $(1/\gamma_0)^{\rm{\#\ of\ sites\ on\ patch}}$}} as it scales as $\gamma_0^{-\lambda}$.  Failure mode 2 can be suppressed \CMH{\it{how?}} \CMH{\sout{to a degree, but at high enough temperature, will eventually happen with high probability, as is the case in the full-measurement version of the protocol .  If too many errors are introduced between measurement cycles,} but at high temperatures} it becomes impossible to correct the system even in principle because the syndrome measurements can no longer be unambiguously decoded.  At sufficiently low temperature, however, \CMH{\sout{with some} under certain} assumptions, our algorithm can extend the lifetime of the system exponentially in system size \CMH{thus leading to a true finite temperature threshold}.

 Suppose that (a) defects are efficiently trapped by the measurement patches, and (b) temperature is low so that there is $\rho \ll 1$ defect pair per measurement patch.  In this regime, \CMH{\sout{condition (a) guarantees that defects do not escape measurement patches.  Then,}} the only error pathway is a sequence of incorrect\CMH{\sout{, but nonetheless ``plausible'' }}error correction operations, whereby some defects are paired with defects that are not their own pair.  
%************************Make explicit here that it's a heuristic argument.  Because the error processes in our model are difficult to etc. etc. etc.
 To upper bound this error rate, note that such erroneous pairing occurs because one member of a paired defect has not yet been measured\CMH{\it{Why must this be true? Can't incorrect pairings occur due to the inexact fusion probability calculation?}.  \sout{In other words, one defect of a pair is measured, and the other defect spends ``too long'' migrating around in the unmeasured bulk region. Suppose that} Define} the average amount of time a defect spends sitting on a measurement patch \CMH{\sout{is} to be} $\tau_s$, and the average time it takes a defect to be detected on a measurement patch, after creation\CMH{\sout{, is} to be} $\tau_d$.  \CMH{\sout{Further suppose} We will consider the regime where} $\tau_s/\tau_d \CMH{\sout{=}\equiv} \delta \ll 1$---\CMH{\sout{that is,} such that} on average\CMH{\sout{,}} defects are unlikely to escape from a measurement patch over the timescale it takes a defect to migrate within the bulk region to a measurement patch.

 \CMH{\sout{Treating the full dynamics of errors is difficult, so we first consider a different, simpler error dynamics.  First, we argue how, in the presence of this simpler error model, our algorithm provides an exponentially long lifetime in system size.  Then, we argue how this simpler error model is actually more pessimistic with respect to possible error processes than the true error dynamics---that is, we expect the real model to have a \emph{better} lifetime scaling than would be expected from the simple error model.}}

 \CMH{\sout{The simple} First we will consider a simplified} error model is defined as follows:  suppose that a single pair of defects is in \CMH{\sout{a} the} system, and that no new pairs will be introduced.  One of the pair is fixed on a measurement rail, and the other is, at time 0, undetected.  \CMH{\sout{Further, suppose that there is an error process that occasionally translates the unmeasured defect by an amount $2\sqrt{\gamma_0 \delta t}$, for hopping rate $\gamma_0$ and for system time $\delta t$.  Note that this means the error process acts on longer distance scales as system time increases.  The particular form of this error process is chosen to mimic a spurious error correction event, where a pair of defects is ``corrected'', but this pair of defects was not a real pair, leaving another unmeasured defect even further away.} We will model surprious error correction by an error process that translates the unmeasured defect by a distance $2\sqrt{\gamma_0 \delta t}$.}  As time increases, the characteristic distance over which this error process could occur also increases, in accordance with the typical pair-wise separation between two defects performing a random walk.  This typical distance is exactly the factor used by the error correction algorithm to determine if a pair of defects should be corrected or not.  Thus, the error process is representative of a worst case error correction event that not only pairs the wrong two defects, but leaves the system in a configuration with an unmeasured defect as far separated from the measured defect as possible.

  \CMH{\sout{If this error process happensevery $\tau_{\epsilon}$, then an} An} uncorrectable error will occur if the bulk defect remains undetected up until it crosses half the system.  For patches of size $\lambda$, the probability that this occurs is roughly $(\tau_{\epsilon} / \tau_d)^{k}$, where $k$ is the number of times the error process must occur for the error process to have separated the defects a distance $(L/2\lambda)$\CMH{, $\tau_{\epsilon}^{-1}$ is the rate of the error process} and $\tau_d$ is the timescale associated with a non-erroneous error correction operation.  \CMH{\sout{Because this error process happens approximately every $\tau_{\epsilon}$, after} After} a timescale $q*\tau_{\epsilon}$, the defect pairs will have been separated a distance \CMH{\sout{$\Sigma^q_{i=1} \sqrt{i * \gamma_0 \tau_{\epsilon}}$,}
 \begin{equation}  
\Sigma^q_{i=1} \sqrt{i * \gamma_0 \tau_{\epsilon}}
\end{equation}
  } assuming that they are never correctly paired.  This sum \CMH{\sout{$\Sigma^q_{i=1} \sqrt{i}$}} grows asymptotically like $q^{3/2}$\CMH{\sout{.  T}, t}hus, $k$ \CMH{\sout{then}} scales approximately like $(L/\lambda)^{2/3}$.\CMH{\sout{new paragraph}} Finally, \CMH{\sout{if we have} assuming there are} $L/\lambda$ such simultaneous \CMH{independent} error processes \CMH{\sout{independently}} in the system---one for each measurement patch---then the total error probability scales like
\begin{align}
\label{eq:err_scaling}
 \CMH{\sout{P(\rm{uncorrectable\ error}) \leq}} (L/\lambda) (\tau_{\epsilon} / \tau_d)^{(L/\lambda)^{2/3}}.
\end{align}
\CMH{\it{no indent}} For this system, $\tau_{\epsilon}$ is much smaller than $\tau_d$, thus the full probability of erroneous corrective operations is exponentially small in system size.

 \CMH{\sout{This probability serves as an upper bound because it is extremely pessimistic about the sorts of error processes occurring} We expect this simple model to overestimate the error rate}.  Note that in the real system, a spurious error correction process that effectively increases the distance between a pair of defects also reduces the total number of defects by two.  Thus, while our toy error model is ``non-interacting''---that is, it assumes $L/\lambda$ independent error processes which, in sum, take the form described in Eq. \ref{eq:err_scaling}---a more careful treatment of the error process, including interactions between defects, as in the real model, would result in an error probability \emph{smaller} than the one calculated here. \CMH{\it{No new paragraph}} In the following section, we provide numerical evidence that the lifetime of the Ising model in the presence of the protocol scales quasi-exponentially \CMH{\it{What does "quasi-exponentially" mean?}} with the number of measurement patches, as anticipated by the upper bound in Eq.\ref{eq:err_scaling}.

@@

In this section, we \CMH{\sout{examine the behaviour of the protocol at different system sizes, temperatures, and measurement fractions} present the numerical simulations of the protocol on finite-size systems of length $L$. We consider systems with unit cells of size $\lambda$ with $\lambda_m=3$ measured sites in each unit cell, and a measurement fraction of $m\equiv \lambda_m/\lambda$.  \sout{While data is reported in terms of system size, the more fundamental length scale is the characteristic size of the \emph{measurement patch}.  This is because the size of the measurement patch is the shortest length scale relevant to the algorithm, and thus controls the majority of the scaling behavior.  Perhaps unsurprisingly, systems of radically different size but with the same number of measurement patches have fairly comparable lifetimes (e.g., size 200 system with 10 patches versus size 100 system with 10 patches).  We elaborate on the scaling of the measurement fractions further in the discussion.  Unless otherwise noted, the data reported here are for systems with 3 measured sites for every 7 sites for a measurement fraction of $3/7$.  Thus, the total size of unit cell is $\lambda=7$, there are $\lambda_m=3$ measured sites, and $\lambda_b=4$ bulk sites, as is depicted in Fig. \ref{fig:detect_swap}.}}

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{LifetimeVsTemperature.pdf}}
\end{center}
\caption{Lifetime \CMH{\it{enhancement}} of \CMH{\sout{various} several} system sizes \CMH{$L$} as a function of temperature\CMH{$T$, using a measurement fraction of $m=3/7$}.   \CMH{\sout{Measurement fraction is $3/7$. Notice the transition between no-effect, and significant lifetime improvement near $T=.16$} Below $T\approx0.16$, we find the lifetime to grow with $L$, indicative of a finite-temperature threshold. \sout{A $3/7$ measurement fraction was used for this data.}\it{ Just use $T$ for the x-axis label}}}
\label{fig:LifetimeVsTemperature}
\end{figure}

\figref{fig:LifetimeVsTemperature} depicts the scaling of the system lifetime \CMH{enhancement} with temperature \CMH{for several system sizes}.  At low temperatures, the system lifetime increases \CMH{\sout{dramatically} monotonically with \sout{with both lower temperatures, and larger}} system size\CMH{, indicating a finite-temperature theshold}.  Due to finite size effects, it is difficult to extract an unambiguous threshold temperature, but below $T\approx\CMH{0}.13$, the lifetime manifestly increases with larger system size.  \CMH{\sout{We empirically define a threshold temperature by the choosing a large system size, fitting a curve to the Lifetime versus Temperature data which results in a lifetime improvement greater than a factor of $10$, and then back-extrapolating where this curve crosses the Temperature axis.} We estimate the threshold by fitting $\Gamma(T)$ for $(\Gamma/\Gamma_0)^{-1} \geq 10$ for the largest system size studied and extrapolating this fit $\Gamma_f$ to define the threshold temperature $T_{\rm{th}}$ by $\Gamma_f(T_{\rm{th}}) = \Gamma_0$. \it{Have you tried computing $T_{th}$ as a function of $1/L$, and then extrapolating to $1/L = 0$? }}

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{LifetimeVsSystemSize.pdf}}
\end{center}
\caption{Lifetime \CMH{enhancement \sout{of the Ising model at various} for } temperatures \CMH{both below and above the threshold \sout{plotted against} as a function of } system size \CMH{$L$, using a measurement fraction $m=3/7$}.  Note the monotonic growth in lifetime \CMH{\sout{for low temperature models} at low temperatures}, as well as the plateau in lifetime for moderately sized systems. \CMH{\sout{A $3/7$ measurement fraction was used for this data.} \it{Can you add lines a guides for the eye? Maybe we should plot this vs. $1/L$?} }}
\label{fig:LifetimeVsSystemSize}
\end{figure}
